### 2011-11-11 trunk/ipmu2012/preliminaries.tex
Update of the proposal section.

\subsection{Possibilistic Variables}
A possibilistic variable $X$ over a universe $U$ is defined as a variable taking exactly one value in $U$, but for which this value is (partially) unknown. The possibility distribution $\pi_X$ gives the available knowledge about the value that $X$ takes. For each $u\in U$, $\pi_X(u)$ represents the possibility that $X$ takes the value $u$.

@@

\subsection{\label{subsec:fuzzy-numbers}Fuzzy numbers and fuzzy intervals}
Dubois and Prade~\cite{Dubois1983} proposed the following definition of \emph{fuzzy interval}.
%\begin{definition}
A fuzzy interval is a fuzzy set $M$ on the set of real numbers $\mathbb{R}$ such that:
\begin{eqnarray}
\forall (u,v)\in\mathbb{R}^2:&\\
\nonumber
\forall w \in [u,v]:&\mu_M(w) \geq\min(\mu_M(u),\mu_M(v))  \\
\exists m \in \mathbb{R}:& \mu_M(m)=1 
\end{eqnarray}
%\end{definition}
If $m$ is unique, then $M$ is referred to as a \emph{fuzzy number}, instead of a \emph{fuzzy interval}. In other words, if the core of a fuzzy interval is a singleton, it can be seen as a fuzzy number. In their work, Dubois and Prade propose four different functions (two possibility and two necessity functions) to asses the position of a fuzzy number N relative to  a fuzzy number M taken as a reference.

@@

\subsubsection{Interval evaluation by ill-known constraints}
The problem of the interval evaluation is explained in \cite{Pon11}: For a crisp interval $I = \left[ a, b \right]$, we want to know if all points in this interval reside between the boundaries of the ill-known interval $\left[ X , Y \right]$, where $X,Y$ are ill-known values on the set of real numbers $\mathbb{R}$, and $\lambda$ is the evaluation function. The following expressions compute the possibility and the necessity:

@@

\paragraph{Example} Consider the ill-known values $X = \left[5, 2, 8\right]$ and $Y = \left[9, 7, 10 \right]$. The knowledge about the evaluation of the interval $\left[a, b \right]$  is given by the expressions \eqref{eq:interval-pos},\eqref{eq:interval-nec}.  Figure~\ref{fig:3d-possibility} shows a 3D plot of the possibility that an interval $[a,b]$ passes the evaluations specified by the ill-known constraints. Note the triangular form for the resulting possibility distribution since the condition $a \leq b$ holds.

\begin{figure}[h!]
\centering
\includegraphics[scale=0.4]{graphs/3D_possibility.eps}
\caption{Possibility of evaluation for the interval $[a,b]$.}
\label{fig:3d-possibility}
\end{figure}
The necessity plot is obtained in a similar way and is shown in Figure~\ref{fig:3d-necessity}. Notice that the necessity measure is not normalized because the supports of $X$ and $Y$ overlap.
\begin{figure}[h!]
\centering
\includegraphics[scale=0.4]{graphs/3D_necessity.eps}
\caption{Necessity of evaluation for the interval $[a,b]$.}
\label{fig:3d-necessity}
\end{figure}

>>>>

%Introductory text:
This background section is dedicated to introduce some basic concepts about possibilistic variables, the differences between fuzzy numbers and intervals. The interval evaluation by means of ill-known constraints is explained.

The preliminaries section concludes with a brief introduction to temporal databases.

\subsection{\label{subsec:possibilistic-variables}Possibilistic Variables}
A possibilistic variable $X$ over a universe $U$ is defined as a variable taking exactly one value in $U$, but for which this value is (partially) unknown. The possibility distribution $\pi_X$ gives the available knowledge about the value that $X$ takes. For each $u\in U$, $\pi_X(u)$ represents the possibility that $X$ takes the value $u$.

@@

\subsection{\label{subsec:fuzzy-numbers}Fuzzy numbers and fuzzy intervals}
Dubois and Prade~\cite{Dubois1983} proposed the following definition of \emph{fuzzy interval}.
\begin{definition}
A fuzzy interval is a fuzzy set $M$ on the set of real numbers $\mathbb{R}$ such that:
\begin{eqnarray}
\forall (u,v)\in\mathbb{R}^2:&\\
\nonumber
\forall w \in [u,v]:&\mu_M(w) \geq\min(\mu_M(u),\mu_M(v))  \\
\exists m \in \mathbb{R}:& \mu_M(m)=1 
\end{eqnarray}
\end{definition}
If $m$ is unique, then $M$ is referred to as a \emph{fuzzy number}, instead of a \emph{fuzzy interval}. In other words, if the core of a fuzzy interval is a singleton, it can be seen as a fuzzy number. In their work, Dubois and Prade propose four different functions (two possibility and two necessity functions) to asses the position of a fuzzy number N relative to  a fuzzy number M taken as a reference.

@@

\subsubsection{Interval evaluation by ill-known constraints}
The problem of the interval evaluation is explained in \cite{Pon11}: For a crisp interval $I = \left[ a, b \right]$, we want to know if all points in this interval reside between the boundaries of the ill-known interval $\left[ X , Y \right]$, where $X,Y$ are ill-known values on the set of real numbers $\mathbb{R}$, and $\lambda$ is the evaluation function.

We assume that $X$ specifies the lower bound and $Y$ the upper bound for a given interval, we want to known whether all points in the interval are larger than or equal to $X$ and smaller than or equal to $Y$. Therefore, we consider two ill-known constraints:

\begin{eqnarray}
C_1\stackrel{\triangle}{=}\left(\leq,X\right)\\
C_2\stackrel{\triangle}{=}\left(\geq,Y\right).
\end{eqnarray}

The following expressions compute the possibility and the necessity:

@@

%\paragraph{Example} Consider the ill-known values $X = \left[5, 2, 8\right]$ and $Y = \left[9, 7, 10 \right]$. The knowledge about the evaluation of the interval $\left[a, b \right]$  is given by the expressions \eqref{eq:interval-pos},\eqref{eq:interval-nec}.  Figure~\ref{fig:3d-possibility} shows a 3D plot of the possibility that an interval $[a,b]$ passes the evaluations specified by the ill-known constraints. Note the triangular form for the resulting possibility distribution since the condition $a \leq b$ holds.
%
%\begin{figure}[h!]
%\centering
%\includegraphics[scale=0.4]{graphs/3D_possibility.eps}
%\caption{Possibility of evaluation for the interval $[a,b]$.}
%\label{fig:3d-possibility}
%\end{figure}
%The necessity plot is obtained in a similar way and is shown in Figure~\ref{fig:3d-necessity}. Notice that the necessity measure is not normalized because the supports of $X$ and $Y$ overlap.
%\begin{figure}[h!]
%\centering
%\includegraphics[scale=0.4]{graphs/3D_necessity.eps}
%\caption{Necessity of evaluation for the interval $[a,b]$.}
%\label{fig:3d-necessity}
%\end{figure}
